---
title: "Tables of simulation results"
author: "Niels Richard Hansen"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r init, echo=FALSE, results='hide'}
library(ggplot2)
ggplot2::theme_set(ggplot2::theme_bw())
knitr::opts_chunk$set(tidy = FALSE, fig.align = 'center')
```

## Using tablorg to manage your simulation study

Have you ever tried to keep track of a larger number of simulation studies? It 
is easy to get lost in the results if you experiment with more than a few 
parameter settings. The purpose of the tablorg package is to help with the 
organization of a larger number of computations,
where code, parameter settings and results should be kept together in an 
accessible way. 

One way to think about tablorg is as a file browser that gives you an overview 
of simulation studies that you are currently doing or that you did in the past.
The unique feature is that you can browse and order the studies according to 
the parameter settings through an HTML interface.

### A simple example


### Coverage study

Suppose you want to study how robust the standard 95% confidence interval 
construction for the mean is to outliers. We do this by implementing a function 
that computes confidence intervals for $B$ trials. The following function does 
this based on the $t$-statistic for the normal distribution.

```{r confConstr}
## x is an n x B matrix
confStand <- function(x) {
  n <- nrow(x)
  mu <- colMeans(x)
  lim <- qt(0.975, n - 1) * apply(x, 2, sd) / sqrt(n)
  data.frame(low = mu - lim, up = mu + lim)
  }

confRob <- function(x) {
  n <- nrow(x)
  mu <- apply(x, 2, median)
  lim <- 1.96 * sqrt(pi / 2) * apply(x, 2, mad) / sqrt(n)
  data.frame(low = mu - lim, up = mu + lim)
  }
```

We can check that for normally distributed random variables, the confidence 
intervals seems to have the correct coverage, that is, the coverage is the 
intended 95%. 

```{r expBase, dependson="confConstr"}
n <- 40
B <- 400
x <- matrix(rnorm(n * B), n, B)
standard <- confStand(x)
robust <- confRob(x)
sum(standard$low < 0 & 0 < standard$up) / B
sum(robust$low < 0 & 0 < robust$up) / B
```

Initially we want to explore what happens if we add a single outlier. We can, 
for instance, investigate the effect on the coverage if one observation is 
considerably larger than the others.

```{r expOut, dependson="expBase", fig.width=6}
m <- 20
outSd <- 1:m
covStand <- covRob <- numeric(m)
xBase <- x[1, ]
for (i in 1:m) {
  x[1, ] <- outSd[i] * xBase
  standard <- confStand(x)
  robust <- confRob(x)
  covStand[i] <- sum(standard$low < 0 & 0 < standard$up) / B
  covRob[i] <- sum(robust$low < 0 & 0 < robust$up) / B
  }
standSd <- sqrt(covStand * (1 - covStand) / B)
robSd <- sqrt(covRob * (1 - covRob) / B)
qplot(outSd, covStand, ymax = covStand + standSd, 
      ymin = covStand - standSd, geom = "ribbon", 
      fill = I("blue"), alpha = I(0.3)) + 
  geom_line() + geom_point() +
  geom_ribbon(aes(ymax = covRob + robSd, 
      ymin = covRob - robSd), fill = "red",
      alpha = 0.3) + 
  geom_line(aes(y = covRob)) + 
  geom_point(aes(y = covRob))
```

Clearly, when the standard deviation of a single observation becomes large 
the coverage increases and approaches 100%. What happes is that the large 
observation inflates the estimate of the (non-robust) standard error, which in 
turn results in too wide confidence intervals and too large a coverage. The 
robust estimators are insensitive to the outlier. Due to the asymptotic 
theory behind the robust choice, the actual coverage is a little below 95%.

We can save the resulting figure from this simulation study and be satisfied 
with our discovery. For future references it is useful to keep track of the code 
and the parameter settings used for the computations. Fortunately, this is easily 
done today in R, as demonstrated by this vignette, using knitr. Simulation 
studies do, however, proliferate because you can make a range of different 
small tweaks and changes of parameters. The result is a collection of knitr 
documents containing code and results for similar computations with minor 
modifications. 

In this coverage example we would like to change the type of outlier distribution 
and the number of outliers. We would also like to change the choice of estimators
for the mean or the standard deviation. In the ideal case we could think up a 
neat design of the study upfront, but in reality, such studies are mostly desgined
in an incremental way. 

## Monitoring progression



























